Kit Theory

### 2023-06-21 paper/paper.tex
Update.

  \subsection{Contributions}
  \begin{enumerate}
  \item
    a multi-sorted approach to extrinsic typing;
  \item
    a multi-sorted extension of McBride's kits to unify renamings and substitutions and their metatheory;
  \item
    a kit abstraction for composition and it's metatheory, unifying the four combinations of renamings and substitutions;
  \item
    a kit abstraction for typing relations, unifying type preservation of renaming and substitution into a single lemma;
  \item
    an Agda-implementation featuring derived term-kits, representation
    independence for substitutions and typing contexts, heterogeneous
    equality, independence of functional extensionality, case studies
    on System F, dependent lambda calculus, pattern matching, linear
    types.
  \end{enumerate}

@@

  \LibCode\KSortTy

@@

  \section{Substitution \& Renamings}
  Our sort-indexed syntax allows us to define substitutions and
  renamings which replace all variables of all sorts simultaneously:

@@

  A renaming \texttt{S₁ →ᵣ S₂} maps variables from \texttt{S₁} to
  variables from \texttt{S₂}.
  A substitution \texttt{S₁ →ₛ S₂} maps variables from \texttt{S₁} to
  terms from \texttt{S₂}.

@@

@@

  \section{Typing}
  \subsection{Library}
  \LibCode\KVariableTyping
  \LibCode\KTyping
  \LibCode\KTypingKit
  \LibCode\KMapTyping
  \LibCode\KLiftTyping
  % \LibCode\KLiftTypingProof
  \LibCode\KSingleTyping
  % \LibCode\KSingleTypingProof
  \LibCode\KTypingNotation
  \LibCode\KTypingTraversal
  \LibCode\KTypingInstances
  % \LibCode\KTypingTraversalNotation
  \subsection{System F}
  \AppCode\FTyping
  \AppCode\FTypingInst
  \AppCode\FPreserve
  \AppCode\FTypingTraversal

>>>>

  \subsection{Contributions}
  \begin{enumerate}
  \item
    a multi-sorted approach to extrinsic typing;
  \item
    a multi-sorted extension of McBride's kits to unify renamings and substitutions and their metatheory;
  \item
    an abstraction for composition and it's metatheory, unifying the four combinations of renamings and substitutions;
  \item
    an abstraction for typing relations, unifying type preservation of renaming and substitution into a single lemma;
  \item
    an Agda-implementation featuring derived term-kits, representation
    independence for substitutions and typing contexts, heterogeneous
    equality, independence of functional extensionality, case studies
    on System F, dependent lambda calculus, pattern matching, linear
    types.
  \end{enumerate}

@@

  For example a term of type \texttt{[𝕖, 𝕥] ⊢ 𝕖} is an expression with two free variables, where variable 0 is a placeholder for an expression, and variable 1 for a type.
  \LibCode\KSortTy

@@

  \section{Renamings \& Substitutions}
  \subsection{Multi-Sorted Renamings \& Substitutions}
  Working with a sort-indexed syntax allows us to define renamings and substitutions
  which replace all variables of all sorts simultaneously:

@@

  A renaming \texttt{S₁ →ᵣ S₂} maps variables from \texttt{S₁} to
  variables from \texttt{S₂}.
  A substitution \texttt{S₁ →ₛ S₂} maps variables from \texttt{S₁} to
  terms in \texttt{S₂}.

@@

  \subsection{Unifying Renamings \& Substitutions}
  A well-known problem with DeBruijn-indices is that full substitution
  cannot be defined directly by structural recursion on the term.
  The typical workaround is to define renamings and substitutions
  separately and use renamings to weaken substitutions when going under binders.

  While this keeps lemmas simple (requiring only structural induction),
  it duplicates the amount of work as all operations and lemmas have
  to be defined and proved for both renamings and substitutions.

  To avoid this duplication,
  McBride\cite{DBLP:journals/jar/BentonHKM12,
  unpublished:mcbride2005kits} introduced \emph{Kits} - an abstraction
  which allows to talk about both renamings and substitutions
  simultaneously.

  The core idea behind kits is that renamings and substitutions only
  differ in what they return:
  \ExampleCode\FExampleSubRen

@@

  \section{Typing}
  % TODO move to typing section
  The only drawback we found, is that types can now also be indexed
  with free expression variables, even though types can never contain
  free variables as assured by the variable constructor. However, this
  only causes minor issues.

  \subsection{Library}
  \LibCode\KVariableTyping
  \LibCode\KTyping
  \LibCode\KTypingKit
  \LibCode\KMapTyping
  \LibCode\KLiftTyping
  % \LibCode\KLiftTypingProof
  \LibCode\KSingleTyping
  % \LibCode\KSingleTypingProof
  \LibCode\KTypingNotation
  \LibCode\KTypingTraversal
  \LibCode\KTypingInstances
  % \LibCode\KTypingTraversalNotation
  \subsection{System F}
  \AppCode\FTyping
  \AppCode\FTypingInst
  \AppCode\FPreserve
  \AppCode\FTypingTraversal
